\textls[-0]{\thetitle}

### 2023-03-23 stlc-linkage-typing-named.tex
revamp figure 8

\begin{figure}
\small
\renewcommand*{\arraystretch}{1.15}
\setlength\tabcolsep{0pt}
\newcolumntype{L}{>{$}l<{$}}
\newcolumntype{C}{>{$}c<{$}}
\newcolumntype{R}{>{$}r<{$}}
%
\colorlet{Bkg-color}{black!8}
\colorlet{Bkg-color-2}{white}
%

@@

\goodTerm{\cdot}{\lkg_0}{\TyLkg{\lsig_0}}

@@

\lsig_1 \coloneqq \LSigAdd{\lsig_0}{\seal_1}{

@@

\goodTerm{\cdot}{\lkg_1}{\TyLkg{\lsig_1}}
\goodTerm{x : \TyTkg{\lsig_0}}{\seal_1}{{
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A1-a}(-0.02,-0.10)(-0.05,0.28)
    A_1
    \tikzmarkend{A1-a}
}{}}

@@

\multirow{-2}{*}{%

@@

@@

\lsig_2 \coloneqq \LSigAdd{\lsig_1}{\seal_2}{

@@

\goodTerm{\cdot}{\lkg_2}{\TyLkg{\lsig_2}}
\goodTerm{x : \TyTkg{\lsig_1}}{\seal_2}{{
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A2-a}(-0.02,-0.10)(-0.05,0.28)
    A_2
    \tikzmarkend{A2-a}
}{}}

@@

@@

\lsig_6 \coloneqq \LSigAdd{\lsig_5}{\seal_6}{

@@

    \tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t6-a}(-0.02,-0.10)(-0.02,0.28)

@@

\goodTerm{\cdot}{\lkg_6}{\TyLkg{\lsig_6}}
\goodTerm{x : \TyTkg{\lsig_5}}{\seal_6}{{
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A6-a}(-0.02,-0.10)(-0.05,0.28)
    A_6
    \tikzmarkend{A6-a}
}}

@@

@@

\lsig_{10} \coloneqq \LSigAdd{\lsig_9}{\seal_{10}}{

@@

\goodTerm{\cdot}{\lkg_{10}}{\TyLkg{\lsig_{10}}}
\goodTerm{x : \TyTkg{\lsig_9}}{\seal_{10}}{{
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A10-a}(-0.02,-0.10)(-0.05,0.28)%
    A_{10}
    \tikzmarkend{A10-a}
}{}}

@@

    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T10-b}(-0.02,-0.45)(-0.02,0.60)

@@

@@

\caption{\TT encoding of the \texttt{STLC} family from \cref{fig:stlc-mechanized}.
Each row $\goodTerm{\mathit{self}\!:\!
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i-cap}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i-cap}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i-cap}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i-cap}%
}$ types a field.
The type $A_i$ controls how the typing of field $t_i$ sees the types of the fields prior to $t_i$.
}
\label{fig:stlc-linkage-typing}
\end{figure}

>>>>

\begin{figure}
\small
\renewcommand*{\arraystretch}{1.15}
\setlength\tabcolsep{0pt}
\newcolumntype{L}{>{$}l<{$}}
\newcolumntype{C}{>{$}c<{$}}
\newcolumntype{R}{>{$}r<{$}}
%
\colorlet{Bkg-color}{black!8}
\colorlet{Bkg-color-2}{white}
%

\begingroup
\renewcommand*{\arraystretch}{1.55}

\fcolorbox{black}{faint-gray}{
\begin{minipage}{25ex}%
\vspace{-1.2ex}%
\begin{gather*}%
\begin{array}{@{}l@{}}
\goodTerm{x :
    \tikzmarkin[disable rounded corners=true,set fill color=P-color,set border color=P-color]{Pi-c}(0.00,-0.15)(0.00,0.30)%
    \TyTkg{\lsig_{i-1}}
    \tikzmarkend{Pi-c}
}{\seal_i}{
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{Ai-c}(0.00,-0.15)(0.00,0.30)%
    A_i
    \tikzmarkend{Ai-c}
}
\\
\goodTerm{\mathit{self} :
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{Ai-b}(0.00,-0.15)(0.00,0.30)%
    A_i
    \tikzmarkend{Ai-b}
}{
    \tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{ti-b}(-0.02,-0.10)(-0.02,0.28)
    t_i
    \tikzmarkend{ti-b}
}{
    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{Ti-b}(0.00,-0.15)(0.00,0.30)
    T_i
    \tikzmarkend{Ti-b}
}
\\
\text{\scriptsize shown below for $i\in\{1,2,6,10\}$}
\end{array} 
\end{gather*}
\end{minipage}
}%
\hfill
\fcolorbox{black}{faint-gray}{
\begin{minipage}{25ex}%
\vspace{-1.2ex}%
\begin{gather*}%
\begin{array}{@{}l@{}}
\lsig_i \coloneq \LSigAdd{\lsig_{i-1}}{x.\seal_i}{\mathit{self}.\,
    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{Ti-a}(0.00,-0.15)(0.00,0.30)
    T_i
    \tikzmarkend{Ti-a}
}
\\
\lkg_i \coloneq \LkgAdd{\lkg_{i-1}}{\mathit{self}.\,
    \tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{ti-a}(-0.02,-0.10)(-0.02,0.28)
    t_i
    \tikzmarkend{ti-a}
}
\\
\goodTerm{\cdot}{\lkg_i}{\TyLkg{\lsig_i}}
\end{array} 
\end{gather*}
\end{minipage}
}%
\hfill
\fcolorbox{black}{faint-gray}{
\begin{minipage}{38.5ex}%
\vspace{-1.2ex}%
\begin{gather*}%
\begin{array}{@{}l@{}}
\TyTkg{\lsig_i} \coloneq \nTySigma{x}{\TyTkg{\lsig_{i-1}}}{\nsub{T_i}{\mathit{self}}{\seal_i}}
\\
\Tkg{\lkg_i} \coloneq \big(\Tkg{\lkg_{i-1}},
    \nsub{t_i}{\mathit{self}}{\nsub{\seal_i}{x}{\Tkg{\lkg_{i-1}}}}\!
\big)
\\
\goodTerm{\cdot}{\Tkg{\lkg_i}}{\TyTkg{\lsig_i}}
\end{array} 
\end{gather*}
\end{minipage}
}
\endgroup

\vspace{2ex}

@@

%&
%\goodTerm{\cdot}{\lkg_0}{\TyLkg{\lsig_0}}

@@

    \mathit{x} : 
    \tikzmarkin[disable rounded corners=true,set fill color=P-color,set border color=P-color]{P0-c}(0.00,-0.15)(0.00,0.30)%
    \tikzmarkend{P0-c}%
    \seal_1
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A1-c}(0.00,-0.15)(0.00,0.30)%
    \tikzmarkend{A1-c}%

@@

\\[2pt]

@@

@@

\\[2pt]
\multirow{-3}{*}{%
\lsig_1 \coloneqq \LSigAdd{\lsig_0}{x.\seal_1}{
    \mathit{self}.\,
    \mathit{self}.\,
%&
%\goodTerm{\cdot}{\lkg_1}{\TyLkg{\lsig_1}}
%&
%\goodTerm{x : \TyTkg{\lsig_0}}{\seal_1}{{
%    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A1-a}(-0.02,-0.10)(-0.05,0.28)
%    A_1
%    \tikzmarkend{A1-a}
%}{}}

@@

    \mathit{x} :
    \tikzmarkin[disable rounded corners=true,set fill color=P-color,set border color=P-color]{P2-c}(0.00,-0.15)(0.00,0.30)%
    \tikzmarkend{P2-c}%
    \seal_2
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A2-c}(0.00,-0.15)(0.00,0.30)
    \tikzmarkend{A2-c}

@@

\\[2pt]

@@

\\[2pt]
\multirow{-3}{*}{%
\lsig_2 \coloneqq \LSigAdd{\lsig_1}{x.\seal_2}{
    \mathit{self}.\,
    \mathit{self}.\,
%&
%\goodTerm{\cdot}{\lkg_2}{\TyLkg{\lsig_2}}
%&
%\goodTerm{x : \TyTkg{\lsig_1}}{\seal_2}{{
%    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A2-a}(-0.02,-0.10)(-0.05,0.28)
%    A_2
%    \tikzmarkend{A2-a}
%}{}}
\\[2pt]

@@

    \mathit{x} :
    \tikzmarkin[disable rounded corners=true,set fill color=P-color,set border color=P-color]{P6-c}(0.00,-0.15)(0.00,0.30)%
    \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
    \tikzmarkend{P6-c}%
    \seal_6
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A6-c}(0.01,-0.10)(-0.02,0.28)
    \tikzmarkend{A6-c}

@@

@@

\\[2pt]

@@

\\[2pt]
\multirow{-4}{*}{%
\lsig_6 \coloneqq \LSigAdd{\lsig_5}{x.\seal_6}{
    \mathit{self}.\,
    \mathit{self}.\,
    \tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t6-a}(-0.02,-0.10)(-0.02,0.25)
%&
%\goodTerm{\cdot}{\lkg_6}{\TyLkg{\lsig_6}}
%&
%\goodTerm{x : \TyTkg{\lsig_5}}{\seal_6}{{
%    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A6-a}(-0.02,-0.10)(-0.05,0.28)
%    A_6
%    \tikzmarkend{A6-a}
%}}
\\[2pt]

@@

    \mathit{x} :
    \tikzmarkin[disable rounded corners=true,set fill color=P-color,set border color=P-color]{P10-c}(0.00,-0.32)(0.00,0.47)%
    \tikzmarkend{P10-c}%
    \seal_{10}
    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A10-c}(0.00,-0.32)(0.00,0.47)%
    \tikzmarkend{A10-c}%

@@

\\[2pt]

@@

    \tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T10-b}(-0.02,-0.45)(-0.02,0.57)

@@

\\[2pt]
\multirow{-5}{*}{%
\lsig_{10} \coloneqq \LSigAdd{\lsig_9}{x.\seal_{10}}{
    \mathit{self}.\,
    \mathit{self}.\,
%&
%\goodTerm{\cdot}{\lkg_{10}}{\TyLkg{\lsig_{10}}}
%&
%\goodTerm{x : \TyTkg{\lsig_9}}{\seal_{10}}{{
%    \tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A10-a}(-0.02,-0.10)(-0.05,0.28)%
%    A_{10}
%    \tikzmarkend{A10-a}
%}{}}
\\[2pt]

@@

%\begin{tabular}{ll}
%  \hline
%  $\TyTkg{\lsig_1} = \nTySigma{\_}{\top}{\TyS{\wcode{\wsig_{\texttt{tm}}}}} $ &  
%  $\TyTkg{\lsig_2} = \nTySigma{\_}{\TyTkg{\lsig_1}}{\El{\wcode{\wsig_{\texttt{tm}}}}}$ \\  
%  $\TyTkg{\lsig_6} = \nTySigma{P_5}{\TyTkg{\lsig_5}}{\CaseSig{\top}{\bot}{\El{\getfield{P_5}{"tm"}} \to \mathit{id} \to \El{\getfield{P_5}{"tm"}}}}$ & \\ 
%  $\TyTkg{\lsig_{10}} = \nTySigma{\_}{\TyTkg{\lsig_9}}{\El{\wcode{\wsig_{\texttt{tm}}}} \to \El{\wcode{\wsig_{\texttt{tm}}}} \to \mathit{id} \to \El{\wcode{\wsig_{\texttt{tm}}}}}$ & \\ 
%\end{tabular}

\caption{\TT encoding of the \texttt{STLC} family from \cref{fig:stlc-mechanized}.
Each row $\goodTerm{\mathit{self}\!:\!
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i-cap}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i-cap}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i-cap}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i-cap}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i-cap}%
}$ types a field.
The type $A_i$ controls how the typing of field $t_i$ sees the types of the fields prior to $t_i$.
}
\label{fig:stlc-linkage-typing}

\end{figure}
